Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-06 documentation/paper.tex
Clarified ML in intro

As part of the PICO-60 experiment, some testing was conducted to determine whether machine learning could be a viable technique to consider for a discrimination function. The results, while not definitive, indicated that the general technique warranted further investigation.

>>>>

As part of the PICO-60 experiment, some testing was conducted to determine whether machine learning (in the form of a multi-layer perceptron) could be a viable technique to consider for a discrimination function. The results, while not definitive, indicated that the general technique warranted further investigation.
